\documentclass[a4paper,8pt]{article}

\usepackage{parskip} 
\usepackage{hologo}
\usepackage{fontspec} % Use only with XeLaTeX/LuaLaTeX
\setmainfont{Liberation Sans}

\usepackage{color}
\usepackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9, top=.4in, bottom=.4in]{geometry}

\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[unicode, hidelinks]{hyperref}
\usepackage{fontawesome5}
\usepackage[normalem]{ulem}
\usepackage[style=authoryear, sorting=ynt, maxbibnames=2]{biblatex}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{1pt}{2pt}{2pt}

\pagestyle{empty}

\begin{document}

\begin{center}
\begin{minipage}{1\textwidth}
\centering
\textcolor[HTML]{1C033C}{\LARGE Narayan Sahu} \\[3pt]
\textcolor[HTML]{4B28A4}{\large Data Engineer | Azure | Snowflake | Bangalore, India} \\[2pt]

{\footnotesize
\setlength{\spaceskip}{0pt} % even tighter word spacing
\textcolor[HTML]{371e77}{
    Phone: 8456890730\hspace{0.3em}|\hspace{0.2em}
    Email: \href{mailto:narayansahu650@outlook.com}{narayansahu650@outlook.com}\hspace{0.3em}|\hspace{0.2em}
    LinkedIn: \href{https://www.linkedin.com/in/dataengineer-narayansahu/}{linkedin.com/in/dataengineer-narayansahu}\hspace{0.3em}|\hspace{0.2em}
    GitHub: \href{https://github.com/Narayan-git/Data_Engineering}{github.com/Narayan-git}
}
}
\end{minipage}
\end{center}




\section{Summary}
\vspace{0.2cm}
\color[HTML]{1C033C}\begin{flushleft} Data Engineer with 4+ years of experience in building scalable ETL pipelines, data warehousing, and reporting solutions using Azure Data Factory, SSIS, Python, SQL Server, Snowflake, and Power BI. Proven success in delivering mission-critical projects for UnitedHealth Group, including DSNP and DMEVS. Recognized for rapid learning, collaboration, and innovation with multiple performance awards for problem-solving, collaboration, and innovation. While my primary strength lies in data engineering, I have also contributed to AI-enabled workflows, including developing a RAG-based chatbot (Clinical Intelligence System) to support healthcare insights. Passionate about leveraging data to drive business insights and operational efficiency.
\end{flushleft}


\section{Technical Skills}
\vspace{0.2cm}
\color[HTML]{1C033C}\textbf{Programming Language:} Python, SQL\\[3pt]
\color[HTML]{1C033C}\textbf{Cloud Platforms:} Azure (Data Factory, Databricks, SQL Database, ADLS Gen2, Blob Storage)\\[3pt]
\color[HTML]{1C033C}\textbf{Data Engineering:} ETL/ELT, SSIS, Azure Data Factory, Airflow, Azure Databricks (PySpark)\\[3pt]
\color[HTML]{1C033C}\textbf{Data Warehousing:} Snowflake, Azure Synapse, Dimensional Modeling (Star \& Snowflake Schema)\\[3pt]
\color[HTML]{1C033C}\textbf{Databases:} SQL Server, Azure SQL, Azure Cosmos DB, Oracle\\[3pt]
\color[HTML]{1C033C}\textbf{Reporting \& Analytics:} Power BI, SSRS\\[3pt]
\color[HTML]{1C033C}\textbf{Version Control \& CI/CD:} Git, Azure DevOps\\[3pt]
\color[HTML]{1C033C}\textbf{Testing Tools:} Pytest, SQL validation scripts\\[3pt]
\color[HTML]{1C033C}\textbf{Job Scheduling:} SQL Server Agent, ADF Triggers, Airflow\\[3pt]
\color[HTML]{1C033C}\textbf{Certifications:} Microsoft Azure Fundamentals (AZ-900)\\[3pt]
\vspace{-0.3cm}



\section{Work Experience}
\vspace{0.2cm}

% ---- Optum India - Data Engineer ----
\noindent
\textbf{Optum India (UnitedHealth Group), Bangalore, India} \hfill \textcolor[HTML]{371e77}{Mar 2024 - Present} \\
\textit{\textcolor[HTML]{371e77}{Data Engineer}}\\[-1.7em]

\begin{itemize}[leftmargin=1.2em, itemsep=1pt, topsep=0pt, parsep=0pt, partopsep=0pt]
    \item Designed and optimized ETL pipelines using Azure Data Factory (ADF), SSIS, and Python, improving daily load performance by \textbf{30\%}.
    \item Implemented data quality checks using Python (Pandas), SQL, and SSIS, increasing data reliability for downstream reporting by \textbf{95\%}.
    \item Integrated and processed multi-source data from Snowflake, Azure Cosmos DB, and SQL Server, handling JSON, CSV, and Excel formats at a scale of over \textbf{1M records per day}.
    \item Reduced verification processing time by \textbf{80\%} by rewriting legacy SSIS workflows and developing Python-based automation packages.
    \item Automated job orchestration using ADF triggers and SQL Server Agent, reducing manual intervention by \textbf{90\%}.
    \item Created Power BI dashboards for monitoring pipeline failures, performance metrics, and SLA adherence.
\end{itemize}
\vspace{-0.5em}

% ---- Optum India - Associate Data Engineer ----
\noindent
\textbf{Optum India (UnitedHealth Group), Bangalore, India} \hfill \textcolor[HTML]{371e77}{Jan 2022 - Feb 2024} \\
\textit{\textcolor[HTML]{371e77}{Associate Data Engineer}}\\[-1.7em]

\begin{itemize}[leftmargin=1.2em, itemsep=1pt, topsep=0pt, parsep=0pt, partopsep=0pt]
    \item Developed ETL pipelines using SSIS and Python (Pandas, NumPy) to support state verification processes.
    \item Built complex SQL views, stored procedures, and triggers for business logic; improved query execution times by \textbf{25\%} through indexing and optimization.
    \item Migrated on-prem workflows to Azure using ADF, ADLS Gen2, Azure SQL, and Logic Apps, improving scalability and reducing compute costs.
    \item Implemented data validation scripts and unit tests (Pytest + SQL) to ensure data consistency across environments.
    \item Collaborated in Agile/Scrum ceremonies and supported QA/UAT phases to ensure smooth releases.
\end{itemize}
\vspace{0em}

% Projects
\section{Projects}
\vspace{0.2cm}

% ---- Work Project 1: DMEVS ----
\noindent
\textbf{DMEVS (Dual Special Needs Plan Medicaid Eligibility Verification System)} 
\hfill 
\textcolor[HTML]{371e77}{Optum India | Jan 2024 - Present} \\
\textit{\textcolor[HTML]{371e77}{ ADF • Python • SSIS • Power BI • SQL Server • Snowflake}}\\[-1.7em]

\begin{itemize}[leftmargin=1.2em, itemsep=1pt, topsep=0pt, parsep=0pt, partopsep=0pt]
    \item Developed secure ETL packages using SSIS and Python to reliably fetch and transfer data from SQL Server and Snowflake.
    \item Built complex SQL views, stored procedures, and triggers to process DSNP Medicaid eligibility data with high accuracy.
    \item Created Power BI dashboards to monitor ETL jobs, pipeline performance, and operational KPIs.
    \item Participated in Agile SCRUM ceremonies, requirement analysis, code reviews, and unit testing to ensure delivery quality.
    \item Supported Integration, QA, UAT, and Production environments for seamless project deployment.
\end{itemize}

\vspace{3.2cm}

% ---- Work Project 2: DSNP ----
\noindent
\textbf{Dual Special Needs Plan (DSNP)} 
\hfill 
\textcolor[HTML]{371e77}{Optum India | Feb 2022 - Dec 2023} \\
\textit{\textcolor[HTML]{371e77}{ SSIS • Python • SQL Server • Oracle • SSRS • Power BI}}\\[-1.7em]

\begin{itemize}[leftmargin=1.2em, itemsep=1pt, topsep=0pt, parsep=0pt, partopsep=0pt]
    \item Implemented ETL pipelines using SSIS and Python (Pandas, NumPy) to process state verification and Medicaid eligibility data.
    \item Built complex views, stored procedures, and triggers across SQL Server, Oracle, and Snowflake databases to meet business requirements.
    \item Developed SSRS and Power BI dashboards to monitor state verification workflows and job performance.
    \item Followed coding guidelines and best practices; supported Integration, QA, and UAT phases.
\end{itemize}

% ---- End-to-End SportsBar Order Data Pipeline ----
\noindent
\textbf{End-to-End SportsBar Order Data Pipeline (Databricks Lakehouse)} 
\hfill 
\textcolor[HTML]{371e77}{\href{https://github.com/Narayan-git/DataEngineeringProjects/tree/main/DataEngineeringProject_EndToEndSportsBarOrderDataPipeline}{github.com/Narayan-git/DataEngineeringProjects}} \\
\textit{\textcolor[HTML]{371e77}{Azure • Databricks • Delta Lake • Apache Spark • Python • SQL}}\\[-1.7em]

\begin{itemize}[leftmargin=1.2em, itemsep=1pt, topsep=0pt, parsep=0pt, partopsep=0pt]
    \item Designed a production-grade \textbf{Medallion Architecture (Bronze–Silver–Gold)} pipeline in Databricks to unify multi-format order data from spreadsheets, WhatsApp exports, cloud drives, and APIs.
    \item Implemented scalable ingestion workflows using \textbf{Spark and Delta Lake}, enabling ACID transactions, schema enforcement, Change Data Feed (CDF), and daily incremental processing.
    \item Developed robust \textbf{data quality and standardization rules} including deduplication, multi-format date parsing, missing value handling, business rule validation, and reference data mapping.
    \item Engineered conformed \textbf{dimension and fact models} (customers, products, pricing, orders) and automated monthly aggregated sales metrics for downstream FMCG analytics.
    \item Orchestrated pipelines using \textbf{Databricks Workflows} and Azure Data Factory, implementing file archival, lineage tracking, and audit-friendly metadata features.
    \item Optimized pipeline performance with partitioning, clustering, and caching strategies, improving read latency and reducing compute cost across daily workloads.
\end{itemize}
\vspace{-0.7em}

% ---- RAG-Based Clinical Intelligence System ----
\noindent
\textbf{RAG-Based Clinical Intelligence System} 
\hfill 
\textcolor[HTML]{371e77}{\href{https://github.com/Narayan-git/DataEngineeringProjects/tree/main/RAG_Based_ClinicalIntelligenceSystem}{github.com/Narayan-git/DataEngineeringProjects}} \\
\textit{\textcolor[HTML]{371e77}{Azure OpenAI • RAG • Embeddings • BM25 • DeepEval • Python}}\\[-1.7em]

\begin{itemize}[leftmargin=1.2em, itemsep=1pt, topsep=0pt, parsep=0pt, partopsep=0pt]
    \item Built a \textbf{Retrieval-Augmented Generation (RAG)} pipeline leveraging a curated knowledge base of 100 NIH clinical documents as the exclusive evidence source for answering medical and genetic queries.
    \item Implemented \textbf{multi-strategy retrieval} including semantic search, hybrid retrieval, and BM25 ranking to ensure high recall and factual relevance across complex clinical topics.
    \item Integrated Azure OpenAI models (\texttt{gpt-4o-mini\_2024-07-18}, \texttt{text-embedding-3-small\_1}) using the \texttt{2025-01-01-preview} API version with project isolation via \texttt{PROJECT\_ID}.
    \item Engineered a \textbf{hallucination-resistant answer generation pipeline} by enforcing strict grounding to retrieved evidence chunks and restricting model outputs to verified clinical sources.
    \item Evaluated pipeline accuracy using \textbf{DeepEval} metrics (faithfulness, relevance, answer correctness), enabling measurable improvements in retrieval and generation reliability.
    \item Designed modular components for ingestion, chunking, embedding creation, vector storage, retrieval orchestration, and LLM-based answer synthesis to support scalable clinical intelligence applications.
\end{itemize}
\vspace{0.0em}


% Education
\section{Education}    
\vspace{0.2cm}
\begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{Master in Computer Application} \newline
    \textcolor[HTML]{371e77}{Fakir Mohan University, Balasore}
    &
    \begin{minipage}[t]{5cm}
        \raggedleft
        \textcolor[HTML]{371e77}{2018 - 2021} \\
        \textcolor[HTML]{4B28A4}{\textit{\textbf{CGPA: 8.2/10}}}
    \end{minipage}
\end{tabularx}\\[-0.5em]

\begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{Bachelor of Computer Applications (BCA)} \newline
    \textcolor[HTML]{371e77}{Berhampur University, Bhubaneswar}
    &
    \begin{minipage}[t]{5cm}
        \raggedleft
        \textcolor[HTML]{371e77}{2015 - 2018} \\
        \textcolor[HTML]{4B28A4}{\textit{\textbf{70\%}}}
    \end{minipage}
\end{tabularx}\\[-0.5em]


% Additional Highlights
\section{Additional Highlights}
\vspace{0.2cm}
\begin{itemize}[nosep, leftmargin=1.2em, itemsep=2pt]
    \item Strong understanding of SDLC, Agile/SCRUM, and Test-Driven Development (TDD)
    \item Excellent communication, problem-solving, and team collaboration skills
    \item Quick learner with a proactive approach to new technologies and challenges
    \item Certified through Optum AI Dojo program and recognized among the Super 30 by Optum's CTO.
\end{itemize}


\end{document}